Functory: A Distributed Computing Library \\ for Objective Caml \thanks{This research was partly supported by the French national project U3CAT (\emph{Unification of Critical C Code Analysis Techniques}, ANR-08-SEGI-021).}

### 2011-09-29 doc/tfp_2011_final/main.tex
*** empty log message ***

The following table shows execution times for various values of $N$
and our three different implementations: \of{Sequential}, \of{Cores}, and
\of{Network}. The purpose of this experiment is to measure the speedup
w.r.t. the sequential implementation.

The first column shows the value of $N$.  The number of tasks is shown in
second column.  Then the last three columns show execution times in
seconds for the three implementations. The figures within brackets
show the speedup w.r.t. sequential implementation.
\begin{center}
  \begin{tabular}{|r|r|r|r|r|r|}
    \hline
    N & D & \#tasks  & \of{Sequential}& \of{Cores}              & \of{Network} 
    \\\hline\hline
    16 &1&   16    &  15.2     &   2.04 (7.45$\times$) &  2.35  (6.47$\times$) 
    \\\hline
       &2&  210    &  15.2     &   2.01 (7.56$\times$) & 21.80  (0.69$\times$)
    \\\hline
    17 &1&   17    & 107.0     &  17.20 (6.22$\times$) & 16.20  (6.60$\times$)
    \\\hline
       &2&  240    & 107.0     &  14.00 (7.64$\times$) & 24.90  (4.30$\times$)
    \\\hline
    18 &1&   18    & 787.0     & 123.00 (6.40$\times$) & 125.00 (6.30$\times$)  
    \\\hline
       &2&  272    & 787.0     & 103.00 (7.64$\times$) & 124.00 (6.34$\times$)  
    \\\hline
    19 &1&   19    &6120.0     & 937.00 (6.53$\times$) & 940.00 (6.51$\times$)  
    \\\hline
       &2&  306    &6130.0     & 796.00 (7.70$\times$) & 819.00 (7.48$\times$)
    \\\hline
  \end{tabular}
\end{center}
From the table above, it is clear that the \of{Cores} and \of{Network}
implementations provide a significant speedup. As evident from the
last row, the speedup is almost 8, which is also the number of
cores we use.  It is also evident from the last column that the
\of{Network} implementation performs significantly better when the
computation time dominates in the total execution time.  The two extreme
cases correspond to the second and the last row: in the second row, the
communication time dominates and is in fact more than 91\%\ of the
total execution time; on the other hand, for the last row
communication time amounts to just 4.6\%\ of the total execution time.
As expected, the network implementation is only beneficial when the
computation time for each individual task is significant, which is the
case in realistic examples.

@@

\paragraph{Acknowledgments.}
The authors are grateful to the ProVal team for support and comments
on early versions of the library and of this paper.

>>>>

The following table shows execution times for various values of $N$
and our three different implementations: \of{Sequential}, \of{Cores}, and
\of{Network}. The purpose of this experiment is to measure the speedup
w.r.t. the sequential implementation.
The first column shows the value of $N$.  The number of tasks is shown in
second column.  Then the last three columns show execution times in
seconds for the three implementations. The figures within brackets
show the speedup w.r.t. sequential implementation.
  \begin{center}
    \begin{tabular}{|r|r|r|r|r|r|}
      \hline
      N & D & \#tasks  & \of{Sequential}& \of{Cores}              & \of{Network} 
      \\\hline\hline
      16 &1&   16    &  15.2     &   2.04 (7.45$\times$) &  2.35  (6.47$\times$) 
      \\\hline
      &2&  210    &  15.2     &   2.01 (7.56$\times$) & 21.80  (0.69$\times$)
      \\\hline
      17 &1&   17    & 107.0     &  17.20 (6.22$\times$) & 16.20  (6.60$\times$)
      \\\hline
      &2&  240    & 107.0     &  14.00 (7.64$\times$) & 24.90  (4.30$\times$)
      \\\hline
      18 &1&   18    & 787.0     & 123.00 (6.40$\times$) & 125.00 (6.30$\times$)  
      \\\hline
      &2&  272    & 787.0     & 103.00 (7.64$\times$) & 124.00 (6.34$\times$)  
      \\\hline
      19 &1&   19    &6120.0     & 937.00 (6.53$\times$) & 940.00 (6.51$\times$)  
      \\\hline
      &2&  306    &6130.0     & 796.00 (7.70$\times$) & 819.00 (7.48$\times$)
      \\\hline
    \end{tabular}
  \end{center}
\begin{figure}[t]
  \vspace*{-4em}
  \begin{center}
    \includegraphics[width=\textwidth]{chart1.pdf}
  \end{center}
  \vspace*{-5em}
  \caption{Speedup ratios for the $N$-queens experiment.}
\label{fig:queens}
\end{figure}
From the table above, it is clear that the \of{Cores} and \of{Network}
implementations provide a significant speedup. As evident from the
last row, the speedup is almost 8, which is also the number of
cores we use.  It is also evident from the last column that the
\of{Network} implementation performs significantly better when the
computation time dominates in the total execution time.  The two extreme
cases correspond to the second and the last row: in the second row, the
communication time dominates and is in fact more than 91\%\ of the
total execution time; on the other hand, for the last row
communication time amounts to just 4.6\%\ of the total execution time.
As expected, the network implementation is only beneficial when the
computation time for each individual task is significant, which is the
case in realistic examples.

@@

\paragraph{Acknowledgments.}
We are grateful to the ProVal team for support and comments
on early versions of the library and of this paper.
We thank the anonymous reviewers for their helpful comments and
suggestions.
